---
title: "My First Report"
author: "Keerit Gill"
format:
  html:
    embed-resources: true
---
## My Notes
This week I learned how to edit and render a **Quarto** document. I also learned the difference between **committing** and **syncing**. I used Claude to help me understand Quarto syntax and fix a preview error, then I verified the results by rendering the report and checking the HTML output myself.

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

```{r}
mean_age <- mean(patients$age)
```

The average age of the patients is `r round(mean_age, 1)` years.

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- Most of the patients are within the ages of 40 and 70 (9) and only 3 patients fall outside this range.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

