---
title: "Assignment 2 Analysis: Mean BMI by Race in NHANES"
author: "Keerit Gill"
format: html
---

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)  # AI-EDIT(2026-06-23): tidyverse-default — consolidated core library() calls into library(tidyverse)
```

## Load Data

```{r}
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
```


## Inspect

```{r}
dim(nhanes)
names(nhanes)
glimpse(nhanes)
colSums(is.na(nhanes))
```

### Missing values in the analysis variables
```{r}

# AI Prompt (Claude): I asked whether na.rm = TRUE in mean_with_n() 
#   was enough to handle missing values. Claude said yes (handles
#   missing BMI values) but suggested adding missing row summary to
#   see how many rows were excluded.
# Verified: Subtracted missing BMI rows from total rows and got 
#   same result as mean_with_n(nhanes$BMI); there were no missing
#   race values
nhanes |>
  summarize(
    total_rows = n(),
    missing_bmi = sum(is.na(BMI)),
    missing_race = sum(is.na(Race))
  )

```

#### The summary excludes 9356 (~8.9%) of all rows. These are all due to missing BMI values. No entries are missing a race value. 96270 rows were used for the BMI-by-race summary.

## Function

```{r}
mean_with_n <- function(x) {
  tibble(
    n = sum(!is.na(x)),
    mean = mean(x, na.rm = TRUE)
  )
}
```

## Summarize

```{r}
mean_with_n(nhanes$BMI)

# AI prompt (Claude): asked how to use mean_with_n() function inside the 
#   pipeline. Claude suggested calling it within summarise() - used below.
# Verified: checked what each line of code was passed and the output,
#   especially following through mean_with_n() argument in summarise().
# AI Prompt (Claude): I asked whether na.rm = TRUE in mean_with_n() 
#   was enough to handle missing values and replace filtering
#   step in pipe. Claude said it was for BMI, but not for Race, but to 
#   keep both filtering steps to be explicit about data filtering. 
# Verified: missing values chunk showed no missing Race values but many 
#   missing BMI values; kept filter in pipe to ensure data filtering
#   was explicit.
bmi_by_race <- nhanes |>
    filter(!is.na(BMI), !is.na(Race)) |>
    group_by(Race) |>
    summarise(mean_with_n(BMI)
    )
bmi_by_race

```

#### The mean BMI across the race groups ranges from 23.7 to 26.1.

## Save Output

```{r}
dir.create("assignments/assignment02-r-with-ai/submission/output", recursive = TRUE, showWarnings = FALSE)
write_csv(bmi_by_race, "assignments/assignment02-r-with-ai/submission/output/summary_table.csv")
```

## AI Audit Note

AI (Claude) used for: 

- explain starter code, step by step 
- debug the summary pipeline
- suggested calling mean_with_n() inside summarise()
- suggested missing values summary

*Asked Github Copilot Chat about how to write a function for average BMI by race but did not use its suggestion